\begin{song}{His Eye Is on the Sparrow}

    \begin{songframe}{v1a}
        Why should I feel discouraged? \\
        Why should the shadows come? \\
        Why should my heart be lonely \\
        And long for heaven and home?
    \end{songframe}

    \begin{songframe}{v1b}
        When Jesus is my portion, \\
        my constant friend is He. \\
        His eye is on the sparrow \\
        and I know He watches me. \\
    \end{songframe}


    \begin{songframe}{ch}
        I sing because I'm happy, \\
        I sing because I'm free, \\
        For His eye is on the sparrow \\
        And I know He watches me.
    \end{songframe}

    \begin{songframe}{v2a}
        ``Let not your heart be troubled'': \\
        His tender words I hear, \\
        And resting on His goodness \\
        I lose my doubt and fear.
    \end{songframe}

    \begin{songframe}{v2b}
        Though by the path He leadeth \\
        but one step I may see, \\
        His eye is on the sparrow \\
        and I know He watches me.
    \end{songframe}

    \begin{songframe}{v3a}
        Whenever I am tempted, \\
        whenever clouds arise, \\
        When songs give place to sighing, \\
        When hope within me dies, \\
    \end{songframe}

    \begin{songframe}{v3b}
        I draw the closer to Him \\
        from care He sets me free. \\
        His eye is on the sparrow \\
        and I know He watches me.
    \end{songframe}

    \verseorder{v1a, v1b, ch, v2a, v2b, ch, v3a, v3b, ch}

    \ccli{77692}
    \creator{Charles Hutchinson Gabriel, Civilla Durfee Martin}
    \legal{Public domain}
\end{song}
\endinput
