\documentclass{article}
\usepackage{fontspec}
\setmainfont{SBL BibLit}

\usepackage{polyglossia}
\setmainlanguage{english}
\setotherlanguages{greek,hebrew}

\usepackage{parskip}
\begin{document}

\section{In the Beginning}

1 In the beginning God created the heaven and the earth.
2 And the earth was without form, and void; and darkness [was] upon the face of the deep. And the Spirit of God moved upon the face of the waters.
3 And God said, Let there be light: and there was light.
4 And God saw the light, that [it was] good: and God divided the light from the darkness.
5 And God called the light Day, and the darkness he called Night. And the evening and the morning were the first day.

\begin{hebrew}
א  בְּרֵאשִׁית, בָּרָא אֱלֹהִים, אֵת הַשָּׁמַיִם, וְאֵת הָאָרֶץ. 
ב  וְהָאָרֶץ, הָיְתָה תֹהוּ וָבֹהוּ, וְחֹשֶׁךְ, עַל-פְּנֵי תְהוֹם; וְרוּחַ אֱלֹהִים, מְרַחֶפֶת עַל-פְּנֵי הַמָּיִם. 
ג  וַיֹּאמֶר אֱלֹהִים, יְהִי אוֹר; וַיְהִי-אוֹר. 
ד  וַיַּרְא אֱלֹהִים אֶת-הָאוֹר, כִּי-טוֹב; וַיַּבְדֵּל אֱלֹהִים, בֵּין הָאוֹר וּבֵין הַחֹשֶׁךְ. 
ה  וַיִּקְרָא אֱלֹהִים לָאוֹר יוֹם, וְלַחֹשֶׁךְ קָרָא לָיְלָה; וַיְהִי-עֶרֶב וַיְהִי-בֹקֶר, יוֹם אֶחָד.  \{פ\} 
\end{hebrew}

\begin{greek}[variant=polytonic]
1 Ἐν ἀρχῇ ἦν ὁ λόγος, καὶ ὁ λόγος ἦν πρὸς τὸν θεόν, καὶ θεὸς ἦν ὁ λόγος. 
2 οὗτος ἦν ἐν ἀρχῇ πρὸς τὸν θεόν. 
3 πάντα δι’ αὐτοῦ ἐγένετο, καὶ χωρὶς αὐτοῦ ἐγένετο οὐδὲ ἕν. ὃ γέγονεν 
4 ἐν αὐτῷ ζωὴ ἦν, καὶ ἡ ζωὴ ἦν τὸ φῶς τῶν ἀνθρώπων· 
5 καὶ τὸ φῶς ἐν τῇ σκοτίᾳ φαίνει, καὶ ἡ σκοτία αὐτὸ οὐ κατέλαβεν. 
\end{greek}

\end{document}
