\documentclass{memoir}
\usepackage{fbb}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{microtype}

\usepackage{xparse}
\NewDocumentCommand{\bibchapter}{ m }{\MakeTextUppercase{#1}\par\bigskip}

\NewDocumentCommand{\bibv}{ m }{\marginpar{\tiny #1}}
\NewDocumentCommand{\bibch}{ m }{\marginpar{\Huge #1}}
\paragraphfootnotes
\renewcommand*{\thefootnote}{\emph{\alph{footnote}}}
\NewDocumentCommand{\bibfn}{ o m }{\footnote[#1]{#2}}
\NewDocumentCommand{\mentioned}{}{\emph} % word used as word
\NewDocumentCommand{\variant}{ m m }{#1\ \mentioned{#2}}

\begin{document}

\bibchapter{Matthew}

\bibch{5}
When Jesus\bibfn[21]{\variant{Gk}{he}} saw the crowds, he went up the mountain;
and after he sat down, his disciples came to him.
\bibv{2} Then he began to speak, and taught them, saying:

\begin{verse}
\bibv{3} ``Blessed are the poor in spirit, 
for theirs is the kingdom of heaven. \\
\bibv{4} ``Blessed are those who mourn, 
for they will be comforted. \\
\bibv{5} ``Blessed are the meek, 
for they will inherit the earth. \\
\bibv{6} ``Blessed are those who hunger and thirst for righteousness, 
for they will be filled. \\
\bibv{7} ``Blessed are the merciful, 
for they will receive mercy. \\
\bibv{8} ``Blessed are the pure in heart, 
for they will see God. \\
\bibv{9} ``Blessed are the peacemakers, 
for they will be called children of God. \\
\bibv{10} ``Blessed are those who are persecuted for righteousness' sake, 
for theirs is the kingdom of heaven. \\
\bibv{11} ``Blessed are you when people revile you and persecute you 
and utter all kinds of evil against you 
falsely\bibfn[22]{Other ancient authorities lack \mentioned{falsely}} on my account.
\bibv{12} Rejoice and be glad, for your reward is great in heaven, 
for in the same way they persecuted the prophets who were before you.
\end{verse}

\bibv{13} ``You are the salt of the earth; but if salt has lost its taste, how can its saltiness be restored?
It is no longer good for anything, but is thrown out and trampled under foot.

\bibv{14} ``You are the light of the world. 
A city build on a hill cannot be hid.
\bibv{15} No one after lighting a lamp puts it under the bushel basket, 
but on the lampstand, and it gives light to all in the house.
\bibv{16} In the same way, let your light shine before others,
so that they may see your good works and give glory to your Father in heaven.''

\end{document}