\documentclass{article}
\usepackage{ebgaramond}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\addtolength{\parindent}{-\parindent}
\addtolength{\parskip}{\baselineskip}

\begin{document}
\Large
NWS Forecast for: Marine On Saint Croix MN\\
Issued by: National Weather Service Twin Cities/Chanhassen, MN\\
Last Update: 7:42 am CDT Oct 17, 2014

\section*{Hazardous Weather Outlook}

Today: A 20 percent chance of showers before 1pm. Cloudy, with a high near 55. Breezy, with a north northwest wind 15 to 20 mph, with gusts as high as 30 mph.

Tonight: Cloudy, with a low around 38. North northwest wind 10 to 15 mph.

Saturday: Mostly sunny, with a high near 52. North wind around 5 mph.

Saturday Night: Mostly clear, with a low around 35. Calm wind becoming south southeast around 5 mph after midnight.

Sunday: A 20 percent chance of showers. Partly sunny, with a high near 59. South wind 5 to 15 mph.

Sunday Night: Mostly clear, with a low around 43. Southwest wind around 5 mph becoming northwest after midnight.

Monday: Mostly sunny, with a high near 57. North northwest wind 5 to 10 mph.

Monday Night: Partly cloudy, with a low around 36. North wind around 5 mph becoming east after midnight.

Tuesday: Sunny, with a high near 55. Southeast wind around 5 mph.

Tuesday Night: Mostly clear, with a low around 38. South southeast wind around 5 mph.

Wednesday: Sunny, with a high near 58. South wind 5 to 10 mph.

Wednesday Night: Partly cloudy, with a low around 40. South wind 5 to 10 mph.

Thursday: A 20 percent chance of showers. Partly sunny, with a high near 59. South southwest wind 5 to 10 mph.


Point Forecast: Marine On Saint Croix MN
 45.21°N 92.76°W (Elev. 702 ft)

Visit your local NWS office at: http://www.crh.noaa.gov/mpx

\end{document}
