% Test of luatex-plain
\parindent=0pt
\hoffset=1in
\hsize=4in

% Palatino font
\font\tenrm=file:Alegreya-Regular at 10pt
\font\numfont=file:Alegreya-Regular at 7pt
\font\titlefont=file:Alegreya-Regular at 14pt
\font\it=file:Alegreya-Italic at 10pt
\font\bf=file:Alegreya-Bold at 10pt
\font\sc=file:AlegreyaSC-Regular at 10pt
\tenrm

\def\title#1{\bigskip\bgroup\titlefont#1\egroup\par}
\def\verse #1 {\bgroup\numfont#1\enspace\egroup}
\def\caption#1{\medskip\bgroup\it#1\egroup\par}
\def\startpoem{\bigskip\begingroup\obeylines} 
\def\endpoem{\endgroup\medskip}
\def\Lord{\bgroup\sc Lord\egroup}
\def\Jah{\bgroup\sc Jah\egroup}

%************************************************************************
\title{Psalm 134}

\caption{A Song of Ascents.}

\startpoem
Come, bless the \Lord!
\verse 2 Come, all you servants of the \Lord,
who stand by night in the house of the \Lord.
\verse 3 Lift up your hands to the holy place, and bless the \Lord.
May the \Lord, maker of heaven and earth, bless you from Zion.
\endpoem

\title{Psalm 23}

\startpoem
The \Lord\ is my shepherd, I shall not want.
\verse 2 He maketh me to lie down in green pastures: 
he leadeth me beside the still waters.
\verse 3 He restoreth my soul: 
he leadeth me in paths of righteousness 
for his names' sake.
\verse 4 Yea, though I walk through the valley 
of the shadow of death, 
I will fear no evil: for thou art with me; 
thy rod and thy staff, they comfort me.

\verse 5 Though preparest a table before me 
in the presence of mine enemies: 
thou anointest my head with oil; 
my cup runneth over.

\verse 6 Surely goodness and mercy shall follow me 
all the days of my life, 
and I will dwell in the house of the \Lord\ forever.
\endpoem

\title{Salmo 130}

\caption{Cántico gradual}

\startpoem
De lo profundo, oh Jehová, a ti clamo.
\verse 2 Señor, oye mi voz;
Estén atentos tus oídos
A la voz de mi súplica.

\verse 3 \Jah, si mirares a los pecados,
¿Quién, oh Señor, podrá mantenerse?
\verse 4 Pero en ti hay perdón,
Para que seas reverenciado.

\verse 5 Esperé yo a Jehová, esperó mi alma;
En su palabra he esperado.
\verse 6 Mi alma espera a Jehová
Más que los centinelas a la mañana,
Más que los centinelas a la mañana.

\verse 7 Espere Israel a Jehová,
Porque en Jehová hay misericordia,
Y abundante redención con él;
\verse 8 Y él redimirá a Israel
De todos sus pecados.
\endpoem

\bye
