% The Tower of Babel
% plain TeX, 2014-09-16

\hoffset	=1in
\voffset	=1in
\hsize		=4in
\vsize		=7in

\font\mainfont		=cmr10 % change to pplr
\mainfont
\font\sc			=cmcsc10
\font\titlefont		=cmr10 scaled \magstep 5
\font\subtitlefont	=cmr10
\font\chapnumfont	=cmr10 at 20pt
\font\versenumfont	=cmr10 at 7pt

\def\title 		#1 	{\bigskip\hfil\bgroup\titlefont#1\egroup\hfil\par}
\def\subtitle	#1 	{\smallskip\hfil\bgroup\subtitlefont\it#1\egroup\hfil\par\bigskip}
\def\chapter 	#1	{\noindent\bgroup\chapnumfont#1\quad\egroup} 		% make boxed drop cap
\def\verse 		#1	{\raise 0.5ex \hbox\bgroup\versenumfont#1\egroup\thinspace} 			

\def\q			#1	{``#1''} % change to allow end punctuation outside of quotes, like csquotes
\def\term		#1	{\bgroup\it#1\egroup} % doesn't work inside footnote
\def\Lord			{\bgroup\sc Lord\egroup}
\def\biblecite #1#2#3 {#1\ #2:\thinspace#3}

%****************************************

\title{The Tower of Babel}

\subtitle{Genesis 11: 1--9}

\chapter{11}
\verse{1}
Now the whole earth had one language and the same words.
\verse{2}
And as they migrated from the east,\footnote{$^a$}{Or {\it migrated eastward}}
they came upon a plain in the land of Shinar and settled there.
\verse{3}
And they said to one another, \q{Come, let us make bricks, and burn them thoroughly.}
And they had brick for stone, and bitumen for mortar.
\verse{4}
Then they said, \q{Come, let us build ourselves a city, and a tower with its top in the heavens, and let us make a name for ourselves;
otherwise we shall be scattered abroad upon the face of the whole earth.}
\verse{5}
The \Lord\ came down to see the city and the tower, which mortals had built.
\verse{6}
And the \Lord\ said, \q{Look, they are one people, and they have all one language; and this is only the beginning of what they will do;
nothing that they propose to do will now be impossible for them.
\verse{7}
Come, let us go down, and confuse their language there, so that they will not understand one another's speech.}
\verse{8}
So the \Lord\ scattered them abroad from there over the face of all the earth, and they left off building the city.
\verse{9}
Therefore it was called Babel, because there the \Lord\ confused\footnote{$^b$}{Heb {\it balal} meaning {\it to confuse}} 
the language of all the earth; and from there the \Lord\ scattered them abroad over the face of all the earth.

\bye
