\documentclass[12pt]{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\renewcommand*{\familydefault}{\sfdefault}

\begin{document}

\section*{Joy}

When I was a little bit bigger than Joy,
when I was a baby,
and when Joy was just littler than she is now,
when she just came out of Mama's tummy,
we took her home.

Joy loves Blue Bunny to sleep with.

\section*{Kentucky}

And then we went to Indiana and Kentucky.
In Kentucky we had hikes
we had a water pail
we built a wooden fire and we cooked hot dogs.
We saw a snake skeleton and we saw a lizard
and we saw a snail.

We had it at home.
I carried it home because I know I like snails
because I like them a lot
and I liked that snail for a pet
because we didn't have any pets in Kentucky 
and that's what I picked out.
And he was afraid of us because he did not like being a pet.
In the morning he hid from us under the table
because he didn't want to see us 
because he thought we were scary.

We swam in the Red River
and then we went home into our cabin.
That river was really cold.

\section*{School}

In the fall I had my first school.
At school I play 
and eat snack 
and have Shabbat.
My friends are Andrew and Kai and Benjamin and Lifka.
But she says funny things.
And Catherine, turns out her real name is Cathy.
My teachers are Miss Shauna, Miss Laura, and Miss Carson.

\section*{Church}

On Sunday we sing songs at church.

\section*{Josie}

I played with Josie.

\section*{Babysitter}

Sometimes JoAnn gives me dinner.

\section*{Play}

I like to play with my crayons and making hats for Joy.

I like to play hide and seek.

\section*{Bobby and Sarah}
Bobby and Sarah ate dinner with us.
And they are going to meet us for lunch.

\end{document}
